---
title: "HW5-93111399-ShervinHakimi"
author: "Shervin Hakimi"
date: "3/16/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1
We will use the Chi Square Goodness of fit for this question.  
We will assume that **they are all from a uniform distribution** and if the goodness of fit gives a significant p value, therefore our assumption that these companies have the same efficiency is correct.


```{r message=FALSE}
#HW5-q1:

Prob = c(0.125,0.125,0.125,0.125,0.125,0.125,0.125,0.125)

q = c(102, 300, 102, 100, 205, 105, 71 , 92)

s = chisq.test(q,p=Prob)
s

```

As we can see the **P-Value** is not significant.  

Therfore our assumption that the companies have the same efficiency is **not correct**.  


## Question 2
In this question because the Classical stores and Modern stores are assumed no to be different in their own groups and that we have a small number of data.  
Therefore we will use the **permutation test** for this question.  
```{r message=FALSE}
#HW5-q2:


mydata = data.frame(score = c(50, 50, 60, 70, 75, 80, 90, 85,55, 75, 80, 90, 105, 65),
                    type = factor(c(rep("A",8), rep("B",6))))

t.test(score~type, data=mydata, var.equal=TRUE)

coin::oneway_test(score~type, data=mydata, distribution="exact")



```
As we can see the **P-Value** is significant.  
Therefore our assupmtion that these two groups aren't different **can be statistically correct**.  

## Question 3
We will use the Willcox test to check whether these groups are different or not.  
We will check whether the **P-Value** is significant or not.  


```{r message=FALSE}

#HW5-q3:
#using willcoxon test:

mydata = data.frame(score = c(509, 517, 502, 629, 830, 911, 847, 803, 727, 853, 757, 730, 774,
                              718, 904,517, 508, 523, 730, 821, 940, 818, 821, 842, 842, 709,
                              688, 787, 780, 901),
                    type = factor(c(rep("A",15), rep("B",15))))

wilcox.test(score~type, data=mydata)





```
The **P-Value** is very significant.  
Therfore our assumption that marketing hadn't any significant influence **can be statistically correct**.  

## Question 4
As we have three different colors whitin stores that are assumed are not  different  we will use the Kruskal-Wallis test.  
We will check our null hypothesis with the pvalue.  
```{r message=FALSE}
#HW5-q4:

mydata = data.frame(score = c(510,720,930,754,105,925,735,753,685,730,745,875,610),
                    type = factor(c(rep("A",5), rep("B",4),rep("C",4))))

kruskal.test(score ~ type, data = mydata)


```
The **P-Value** is significant.  
Therefore the assumption that the colors don't have influence **can be statistically correct**.

## Question 5 
In this question we will use the friedman rank sum test because we want to test the differences in multiple months.  
We will check our null hypothesis that these months aren't different with our resulting p-value.  
```{r  eval = FALSE, message = FALSE}
#HW5-q5:
mydata = read.csv("/Users/shervin/Downloads/hw_05/data/tv.csv")

friedman.test(mydata,c("March"	,"April"	,"May"	,"Jun"))


Sample<-matrix(c(mydata$April,mydata$March,mydata$May,mydata$Jun),ncol=4)

friedman.test(Sample)

```
```{r eval=FALSE}
Friedman rank sum test

data:  Sample
Friedman chi-squared = 1.2, df = 3,
p-value = 0.753

```

As we can see the **P-Value** is significant.  
Therefore the assumption that the marketing had an effect don't have influence **can be statistically correct**.

## Question 6
We have three different features with three different groups.  
Therefore using chi-square independence test is a good test for this dataset.  
We will check our null hypothesis using the pvalue.  
```{r message=FALSE}
#HW5-q6:

mydata = matrix(
    c(151,802,753,252,603,55,603,405,408),
    nrow = 3,
    ncol = 3
)

rownames(mydata) <- c("Small","Medium","Large")
colnames(mydata) <- c("Always","Sometime","Never")

chisq.test(mydata)
```
The **P-Value** is very low.  
Therefore our assumption that population doesn't have an influence on consumption is **not correct**.  

## Question 7 
Considering the given data and the given question on whether the random samples of the two products have different sales?  

We will use the Spearman correlation test and check this assumption using the pvalue.  


```{r message=FALSE}
# HW5-q7
mydata = read.csv("/Users/shervin/Downloads/hw_05/data/consumption.csv")


cor.test( ~ A + B, 
          data= mydata,
          method = "spearman",
          continuity = TRUE,
          conf.level = 0.95)


```
As we can see the **P-Value** is significant.  
Therefore our null hypothesis that the two sales are not statistically correlated **can be correct**.

## Question 8 
In this question like question 6 we will use the chi-square independence test to see whether the gender has an influence.  
We will check the pvalue to check our null hypothesis
```{r}
#HW5-q8:


mydata = matrix(
  c(301,353,558,502,155,153),
  nrow = 3,
  ncol = 2
)

rownames(mydata) <- c("Price","Design","Color")
colnames(mydata) <- c("Male","Female")

chisq.test(mydata)
```
The **P-Value** is very low.  
Therefore our null hypotehsis is **not correct**.
